Galaxy Zoo: Morphological Classifications for 120,000 Galaxies in HST Legacy Imaging

### 2016-05-31 writeup/gz_hubble_data.tex
New version of Figure 12. Closes #158.

Figure~\ref{fig:sankey} shows the breakdown of morphologies for the combined
surveys in GZH as a flow~diagram, where each node represents a task and the
flows between the nodes represent the possible responses. The width of the
flows is proportional to the number of galaxies associated with that response.
Figure~\ref{fig:sankey} uses a simple plurality vote to assign the combined set
of labels for each galaxy. This method is likely to undersample some of the
categories; visual inspection of images suggests that \ffeatures$\gtrsim0.3$
identifies disk-dominated or irregular galaxies reliably, for example. This
method also does not use the suggested thresholds in
Table~\ref{tbl:thresholds}.

\begin{figure*}
\center
\includegraphics[width=0.90\textwidth]{figures/sankey_both.png}
\caption{Demographics of the morphologies for all galaxies in GZH (including
both \hst{} and SDSS imaging). Each node in each diagram (dark blue horizontal
bars of uniform height) represents a task in the tree. The left diagram shows
the full decision tree. The right diagram zooms in on the features/clumpy
tasks, which are otherwise difficult to see. The paths between tasks represent
each possible answer to the task, flowing from top to bottom between their
origin and the subsequent task in the tree. Labels are assigned to
each galaxy based on the plurality answer for each task. A galaxy is assigned
only one label at each node. Widths of the paths are proportional to the number
of galaxies assigned to that path. The widths of the nodes are proportional to
the number of galaxies for which the question was reliably answered.}
\label{fig:sankey}
\end{figure*}

Given these caveats, the overall distribution of galaxy types is significantly
different than the low-redshift sample classified in SDSS imaging from GZ1 and
GZ2. \citet{lin11} found that elliptical galaxies exceeded spiral galaxies by a
factor of $\sim2:1$ in their spectroscopic sample if using a plurality vote
criterion (although \citealt{bam09} show that this strongly depends on the
selection method; spirals are the dominant population in a volume-limited
sample at $z<0.088$, for example). The weighted votes for GZH have smooth
galaxies outnumbering disks and clumpy galaxies by a factor of $\sim3:1$,
however. The fraction of objects identified as stars or artifacts is also much
higher in the \hst{} imaging. By plurality votes, these encompass only
$\sim0.1\%$ of images in SDSS \citep{wil13}, but 6\% of images in GZH.

Within the sample of galaxies identified as ``not smooth'', it is clear that
the addition of the clumpy branch is necessary to describe a large fraction of
the sample, since disk-dominated galaxies outnumber clumpy morphologies by less than
a factor of 2. Disk galaxies are primarily unbarred \citet{mel14} and
possessing two visible spiral arms over a flat distribution of pitch angles and
bulge prominence. Clumpy galaxies are identified across the full range of clump
multiplicities, with the exception of 1-clump galaxies (which would be
difficult to differentiate from compact spheroids). Roughly half of the
galaxies have at least 1~clump identified as the brightest. Clumps are most
commonly asymmetrically arranged in clusters and are not often seen embedded in
larger structures.

>>>>

As an example of visualising the overall morphological distribution,
Figure~\ref{fig:sankey} shows the breakdown of GZH morphologies as a flow
diagram. In order to show a physically meaningful sample,
Figure~\ref{fig:sankey} only includes images from a volume-limited sample
($z<1.0, m_\mathrm{I}<22.5$) in a single \hst{} survey (COSMOS, which has the
largest number of total galaxies).  We use a simple plurality vote for the
responses to each task to characterise the morphologies.  This emphasises one
of the basic results of the GZH project; namely, that there are comparable
numbers of spheroid and disk galaxies in the Universe at $z\sim1$, with
significant diversity in the arrangement of spiral arms and internal clumps.

\begin{figure*}
\center
\includegraphics[width=0.90\textwidth]{figures/sankey_cosmos.pdf}
\caption{Demographics of the morphologies for GZH from a volume-limited
sample ($z<1.0, m_\mathrm{I}<22.5$) of the COSMOS galaxies. Each node in the diagram (dark blue horizontal
bars of uniform height) represents a task in the tree (Figure~\ref{fig:decisiontree}). The left diagram shows
the full decision tree. The right diagram zooms in on the features/clumpy
tasks, which are otherwise difficult to see. Paths between tasks represent
each possible answer to the task, flowing from top to bottom between their
origin and the subsequent task in the tree. Labels are assigned to
each galaxy based on the plurality answer for each task. A galaxy is assigned
only one label at each node. Widths of the paths are proportional to the number
of galaxies assigned to that path. The widths of the nodes are proportional to
the number of galaxies for which the question was reliably answered.}
\label{fig:sankey}
\end{figure*}

The overall distribution of galaxy types is significantly different than the
low-redshift sample classified in SDSS imaging from GZ1 and GZ2. \citet{lin11}
found that elliptical galaxies exceeded spiral galaxies by a factor of
$\sim2:1$ in their spectroscopic sample when using a plurality vote criterion
(although \citealt{bam09} show that this strongly depends on the selection
method; spirals are the dominant population in a volume-limited sample at
$z<0.088$). The data for GZH show that smooth galaxies have a comparable total
population to ``featured'' galaxies of which roughly 20\% are dominated by
clumps rather than well-organized disks.  The fraction of objects identified as
stars or artifacts is also much higher in the \hst{} imaging. By plurality
votes, these encompass only $\sim0.1\%$ of images in SDSS \citep{wil13}, but
6\% of images in GZH.

Within the sample of galaxies identified as ``not smooth'', it is clear that
the addition of the clumpy branch is necessary to describe a large fraction of
the sample, since disk-dominated galaxies outnumber clumpy morphologies by less than
a factor of 2. Disk galaxies are mostly unbarred \citep{mel14} and
possess two visible spiral arms over a flat distribution of pitch angles and
bulge prominence. Clumpy galaxies are identified across the full range of clump
multiplicities, with the exception of 1-clump galaxies (which would be
difficult to differentiate from compact spheroids). Roughly half of the
galaxies have at least 1~clump identified as the brightest. Clumps are most
commonly asymmetrically arranged in clusters and usually embedded within
larger objects.
